%_____________________________________________________________________________________________ 
% A Holistic Approach to Autonomic Self-Healing Cloud Computing Architecture
% Abstract Page
% Fri Apr 19 12:50:42 IST 2013
%___________________________________________
\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
Cloud computing systems are prone to errors and faults and a major amount of task is wasted in maintaining the system and bring it back to a stable state after a fault. Human resources in the cloud computing architecture currently handle this maintenance. Despite the emergence of ultra-reliable components, failure in cloud computing systems is still an unmitigated problem. As a result of this a lot of resources in the form of money and manpower and efforts in the form of man months is wasted. The proposed mechanism focuses efforts to make a cloud-computing environment reliable and robust by proposing an autonomic, self-healing architecture. We adopt a holistic approach to the problem and aim at proposing an architecture that is general enough to be adopted by a wide range of existing systems. Some of the major challenges include selecting the appropriate actions for healing and reducing the overhead thus making healing lightweight and transparent, yet effective. The proposed system architecture makes use of data mining techniques to generate rules based on gathered system data from logs. The rules are used to make decisions of corrective action and hence carry out the self-healing mechanism.
%Missing wikipedia citation.
\end{abstract}
%_____________________________________________________________________________________________ 

